Draft Report

### 2020-11-18 DraftReport.Rmd
update on model 3 spacing etc

A plot that shows the relationship between different policies vs case rate.
```{r}
df %>% 
  ggplot(aes(x = mask_public_bool, y = case_rate_100k, color = case_rate_100k)) + 
  geom_point(aes(size=case_rate_100k)) + 
  labs(
    title = 'Case Rate vs Mask Public Mandate', 
    x = 'Mask Mandate in Public', 
    y = 'Case Rate', 
    color = 'Case Rate'
  )
```
#### Model 3-a
Next, the linear model is created from model 2 with the mask policy variables added for the regression. The regression coefficient shows that Mask_public_bool variable is highly significant. The result suggests that public mask mandate policy has postive effect in bringing the case number down.

```{r}
model3a <- lm(case_rate_100k ~ log10(population_density)
              + poverty_pct
              + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)
```
#### Model 3-b&c
Considering that there could be multiple policy variables that are relevant to predicting the case number. We have also examined the "Closed.other.non.essential.businesses" variable (renamed as "business_closed") which represents the date when the state issued closure of non-essential businesses. As "business_closed" is a date variable, a transformation was performed to convert the date into a variable "business_close_diff" which represents the days difference between the business close date of the state compared to the average date of all the states.
```{r}

@@

From the plot of business close date difference against case rate, the graph shows that there is some degree of linearity between the two variables.
```{r warning=FALSE}
df %>% 
  ggplot(aes(x = business_close_diff, y = case_rate_100k, color = business_close_diff)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  labs(
    title = 'Case Rate vs Mask Public Mandate', 
    x = 'Non-Essential Business Close Date difference compared to Average', 
    y = 'Case Rate', 
    color = 'Case Rate'
  )
```

By running the model with "business_close_diff" against case rate variable, the coefficient shows that the variable is significant.
```{r}
model3b <- lm(case_rate_100k ~ business_close_diff, data = df)
coeftest(model3b, vcov = vcovHC)
```
However, the regression with both policy variables "mask_pubic_bool" and "business_close_diff" shows that neither the the variable is significant. 
```
model3c <- lm(case_rate_100k ~ business_close_diff + mask_public_bool, data = df)
coeftest(model3c, vcov = vcovHC)
```

>>>>

A plot that shows the relationship between different policies vs case rate.
```{r}
df %>% 
  ggplot(aes(x = mask_public_bool, y = case_rate_100k, color = case_rate_100k)) + 
  geom_point(aes(size=case_rate_100k)) + 
  labs(
    title = 'Case Rate vs Mask Public Mandate', 
    x = 'Mask Mandate in Public', 
    y = 'Case Rate', 
    color = 'Case Rate'
  )
```

#### Model 3-a
Next, the linear model is created from model 2 with the mask policy variables added for the regression. The regression coefficient shows that Mask_public_bool variable is highly significant. The result suggests that public mask mandate policy has postive effect in bringing the case number down.

```{r}
model3a <- lm(case_rate_100k ~ log10(population_density)
              + poverty_pct
              + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)
```

#### Model 3-b&c
Considering that there could be multiple policy variables that are relevant to predicting the case number. We have also examined the "Closed.other.non.essential.businesses" variable (renamed as "business_closed") which represents the date when the state issued closure of non-essential businesses. As "business_closed" is a date variable, a transformation was performed to convert the date into a variable "business_close_diff" which represents the days difference between the business close date of the state compared to the average date of all the states.
```{r}

@@

From the plot of business close date difference against case rate, the graph shows that there is some degree of linearity between the two variables.
```{r warning=FALSE}
df %>% 
  ggplot(aes(x = business_close_diff, y = case_rate_100k, color = business_close_diff)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  labs(
    title = 'Case Rate vs Non-Essential Business Close Date difference compared to Average', 
    x = 'Non-Essential Business Close Date difference compared to Average', 
    y = 'Case Rate', 
    color = 'Case Rate'
  )
```

By running the model with "business_close_diff" against case rate variable, the coefficient shows that the variable is significant.

```{r}
model3b <- lm(case_rate_100k ~ business_close_diff, data = df)
coeftest(model3b, vcov = vcovHC)
```

However, the regression with both policy variables "mask_pubic_bool" and "business_close_diff" shows that neither the the variable is significant. 
```{r}
model3c <- lm(case_rate_100k ~ business_close_diff + mask_public_bool, data = df)
coeftest(model3c, vcov = vcovHC)
```
